---
title       : Titanic Survivor Analysis
subtitle    : Data Analysis and Survivor Prediction Modelling
author      : Nikhil W
job         : Dev Data Products - DataScienceCourse
framework   : revealjs        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : monokai      # tomorrow
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---


## Titanic Survivor Analysis
<br/>
<br/>

Nikhil W

<span style="color:gray;">Developing Data Products - Project</span>


---
### Project Overview
The objective for this project is to develop a model for prediciting passgenger survival on the Titanic accident.


Lets look at the train dataset available to us.
```{r  message=FALSE, warning=FALSE}
library(ggplot2)
dtrain <- read.csv("train.csv")

```
```{r, fig.height=5}
str(dtrain)
```



---
### Data Visualization
In order to better understand the relationship between different variables in the dataset, let's plot relationship between Passenger Class, Gender and Survived (0 or 1).
```{r fig.height=6, fig.width=15}
g <- ggplot(data = dtrain, aes(Sex, fill=factor(Survived, labels =c("Perished","Survived")))) + geom_bar() 
g + facet_grid(.~ Pclass)
```

<span style="font-size:26px;">From above we can infer that male passengers from 3rd class cabin were among the most perished. Female passengers across all Cabin Classes survived the most.</span>

---

### Model Generation

<div align="left">
Here we'll utilize 2 classification Models :
<br/>
1. RPart
</div>
```{r eval=FALSE, tidy=TRUE}
rpart(formula = as.factor(Survived)~Sex+Parch+SibSp+Pclass+Fare+Embarked,data = dtrain, control = rpart.control(minsplit = 10, cp =  0.01), na.action= na.exclude)


```

```{r eval=FALSE, tidy=TRUE}
Confusion Matrix and Statistics

          Reference
Prediction   0   1
         0 521 130
         1  28 212
                                         
         Accuracy : 0.8227 
```
          

<div align="left">
2. RandomForest
</div>
```{r eval=FALSE, tidy=TRUE}
randomForest(formula = as.factor(Survived)~Sex+Parch+SibSp+Pclass+Fare+Embarked,data = dtrain, mtry = 5, nodesize = 10, ntree=500, na.action= na.exclude)
```

```{r eval=FALSE, tidy=TRUE}
Confusion Matrix and Statistics

          Reference
Prediction   0   1
         0 526  77
         1  23 265
                                          
         Accuracy : 0.8878 
```


---

## Summary

Looking at the results of previous models we can conclude that the RandomForest Model yields higher accuracy of <span style="color:orange;">88.78%</span>.
<br/>
<br/>

Couple Points to remember :
- The model can be further improved by varying the tuning parameters <span style="color:cyan;">mtry, nodesize & ntree</span>.
- The current model is validating against Train dataset, which can cause overfitting.
- To improve the model the trainset can be split into Train and Validate sets.




